Computable Compressed Matrices\\Suplementary Material

### 2013-11-29 manuscript.tex
atualizacao

% Please keep the abstract between 250 and 300 words
\section*{Abstract}
The biggest cost of
computing with large matrices in any modern computer is related to memory
latency and bandwidth. The average latency of modern RAM reads is 150 times
greater than a clock step of the processor\cite{alted2010modern}. Throughput is
a little better but still 25 times slower than the CPU can consume. The
application of bitstring compression allows for larger matrices to be moved
entirely to the cache memory of the computer, which has much better latency and
bandwidth (average latency of L1 cache is 3 to 4 clock steps). This allows for
massive performance gains as well as the ability to simulate much larger models
efficiently. In this work, we propose a methodology to compress matrices in such
a way that they retain their mathematical properties. Considerable compression
of the data is also achieved in the process Thus allowing for the computation of
much larger linear problems within the same memory constraints when compared
with the traditional representation of matrices.
% Please keep the Author Summary between 150 and 200 words
% Use first person. PLoS ONE authors please skip this step. 
% Author Summary not valid for PLoS ONE submissions.   
\section*{Author Summary}

@@

As a test methodology, all the described operations were also compared to traditional methods. The matrix dimensions n x 
n used were $n = 1,000$, $6,000$, $11,000$ to $20,000$. We emphasize that the first matrix,  created with a 1,000 
dimension has $10^6$ elements, while the one with a 20,000 dimension has $4 \times 10^8$ elements. With the increase of 
the size of the matrices, a larger amount of memory must be reserved to allocate the numbers. The compression effect of 
the matrices can be verified in the results since by the proposed method the matrix is ​​directly loaded into the main 
memory, avoiding the need for access to the secondary memory.

@@

Falar dos dados do GraphLab, os usados foram o do netflix, e medir o tempo 
médio da executacao por umas 10 vezes.

Os dados utilizados nos testes realizados estão disponíveis em XXX. Esses dados 
correspondem a ....

>>>>

% Please keep the abstract between 250 and 300 words
\section*{Abstract}
The biggest cost of
computing with large matrices in any modern computer is related to memory
latency and bandwidth. The average latency of modern RAM reads is 150 times
greater than a clock step of the processor\cite{alted2010modern}. Throughput is
a little better but still 25 times slower than the CPU can consume. The
application of bitstring compression allows for larger matrices to be moved
entirely to the cache memory of the computer, which has much better latency and
bandwidth (average latency of L1 cache is 3 to 4 clock steps). This allows for
massive performance gains as well as the ability to simulate much larger models
efficiently. In this work, we propose a methodology to compress matrices in such
a way that they retain their mathematical properties. Considerable compression
of the data is also achieved in the process Thus allowing for the computation of
much larger linear problems within the same memory constraints when compared
with the traditional representation of matrices.

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLoS ONE authors please skip this step. 
% Author Summary not valid for PLoS ONE submissions.   
\section*{Author Summary}

@@

As a test methodology, all the described operations were also compared to traditional methods. The matrix dimensions n x 
n used were $n = 10$, $100$, $1,000$, $10,000$, $20,000$ to $100,000$, by $10,000$. We emphasize that the matrix,  
created with a 1,000 dimension has $10^6$ elements, while the one with a 100,000 dimension has $1 \times 10^{10}$ 
elements. With the increase of the size of the matrices, a larger amount of memory must be reserved to allocate the 
numbers. The compression effect of the matrices can be verified in the results since by the proposed method the matrix 
is ​​directly loaded into the main memory, avoiding the need for access to the secondary memory.

Inserir os resultados

@@

Inserir o segundo conjunto de resultados aqui.
